COG-ED Manuscript

### 2022-01-13 06_Paper/COG-ED/Manuscript.Rmd
started coding lower plot for pipelines

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
    geom_point() +
    geom_line() +
    theme_classic() +
    labs(x = NULL, y = "Fixed effects estimate") +
    scale_y_continuous(position = "right") +
    theme(axis.text.x = element_blank())

>>>>

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
    geom_point(data = sca_results, aes(x = num, y = sign, color = predictor, group = predictor)) +
    geom_line() +
    geom_text(aes(x = length(pipelines_data)-2, y = -0.01, label = "NFC")) + 
    geom_text(aes(x = length(pipelines_data)-2, y = -0.12, label = "Level")) +
    theme_classic() +
    labs(x = NULL, y = NULL) +
    scale_y_continuous(position = "right") +
    ggtitle("Fixed effects estimate") +
    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1), legend.position = "none")

  # add columns to the data frame that describe the pipeline

  sca_results$Dim <- ifelse(substr(sca_results$pipeline,1,2) == "AA", 2,
                            ifelse(substr(sca_results$pipeline,1,2) == "AW", 3,
                                   ifelse(substr(sca_results$pipeline,1,2) == "AW", 3,
                                          ifelse(substr(sca_results$pipeline,1,2) == "WW", 4,
                                                 ifelse(substr(sca_results$pipeline,1,2) == "WA", 5, NA)))))
  sca_results$Trans <- ifelse(substr(sca_results$pipeline,3,3) == "R", 7,
                              ifelse(substr(sca_results$pipeline,3,3) == "L", 8,
                                     ifelse(substr(sca_results$pipeline,3,3) == "L", 8,
                                            ifelse(substr(sca_results$pipeline,3,3) == "I", 9,
                                                   ifelse(substr(sca_results$pipeline,3,3) == "S", 10, NA)))))
  sca_results$Excl <- ifelse(substr(sca_results$pipeline,4,4) == "N", 12,
                             ifelse(substr(sca_results$pipeline,4,4) == "2", 13,
                                    ifelse(substr(sca_results$pipeline,4,4) == "5", 14,
                                           ifelse(substr(sca_results$pipeline,4,4) == "3", 15,
                                                  ifelse(substr(sca_results$pipeline,4,4) == "O", 16, 
                                                         ifelse(substr(sca_results$pipeline,4,4) == "T", 17, NA))))))

  sca_lowerplot <- ggplot(data = sca_results) +
    geom_point(aes(x = num, y = Dim, color = "red")) +
    geom_point(aes(x = num, y = Trans, color = "blue")) +
    geom_point(aes(x = num, y = Excl, color = "purple")) +
    theme_classic() +
    labs(x = NULL, y = NULL) +
    scale_y_reverse() +
    theme(axis.text.x = element_blank(), axis.text.y = element_blank(), legend.position = "none")
